Towards Attack-Tolerant Networks: Concurrent Multipath Routing and the Butterfly Network

### 2017-10-31 www-2018/source/paper.tex
Update discussion and conclusion.

Our main contributions are:
\begin{itemize}
\item{
We propose a novel structured multipath fault tolerance (SMFT) scheme
for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
We do so by modeling redundant {\em independent paths}
with {\em bounded trust transitivity} as a single virtual channel,
and show that the probability of detecting adversarial faults
approaches 1 exponentially with the number of paths;
}
\item{We prove that the number of $h$-internal vertex disjoint
paths between two nodes in a wrap-around butterfly network
increases exponentially with $h$,
and thus that the number of independent paths in a network
increases exponentially with the level of trust transitivity;
}
\item{We present a scalable and efficient concurrent
multipath routing (CMR) algorithm on the butterfly network topology,
which can be combined with SMFT to achieve a high level of attack tolerance.}
\end{itemize}

@@

Standard fault tolerance methods use redundancy to detect and correct
statistically indpendent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta_h$ direct channels, with indpendent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta_h$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

@@

In a more sophisticated multipath fault tolerance scheme,
Alice randomly chooses $k \leq \delta_h$ channels and sends a copy of
her message on each.
We assume that Mal is capable of compromising $l \leq \delta_h$ channels.
Since Alice chooses channels randomly,
all channels are equally likely to contain a message,
so Mal can do no better than also choosing randomly.
If $k > l$, at least one message will get through uncompromised and all
errors are detectable.
Otherwise, the probability of Mal producing an undetectable error is
the probability that all of Alice's chosen channels are compromised:
\beq
\label{eq:pf}
p_f &=& \frac{l!(\delta_h-k)!}{\delta_h!(l-k)!}.
\eeq
Letting $k=\alpha \delta_h$ and $l=\beta \delta_h$, then applying Stirling's
approximation gives:
\begin{eqnarray}
\label{eq:pf_approx}
p_f &\approx&
\frac{\sqrt{\beta(1-\alpha)}}{\sqrt{\beta-\alpha}}
\left[
    \left( \frac{\beta-\alpha}{1-\alpha} \right)^{\alpha}
    \left( \frac{\beta}{\beta-\alpha} \right)^{\beta}
    (1-\alpha)
\right]^{\delta_h}.
\end{eqnarray}

Figure \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Equation (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta_h$.
This result is significant because,
as we will soon show, $\delta_h$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}
In other words, this scheme exhibits a {\em stabilizing asymmetry}:
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta_h$.

\begin{figure}
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
message copies and the number of adversarial faults.
}
\label{fig:pfail}
\end{figure}

@@

So far, we have assumed that Alice and Bob have access to some number
$\delta_h$ of channels with statistically indpendent faults.
However, in real communication architectures, direct links between all
pairs of individuals are intractable and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer uncorrelated: two paths may pass through the
same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

Trust-based approaches to secure communication assume that some parties
cannot be compromised.
One common approach, the web of trust
\cite{zimmermann_official_1995,ferguson_practical_2003},
extends trust infinitely transitively:
Alice trusts her friends, as well as her friends' friends, and so on.
However, the assumption of infinitely transitive trust is unrealistic
\cite{christianson_why_1997}.
Furthermore, infinite trust transitivity does not allow for analysis of
network strucutre; all that matters is whether some path exists,
rather than the number of paths and their structure.

An alternative assumption might be that each hop away from Alice in
in the network
reduces the probability that a node can resist compromise exponentially.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
The above model can be further
simplified by assuming that nodes up to some fixed number
of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

@@

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communicaiton
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.

@@

Our goal is to achieve fault tolerance through redundancy.
In the network setting, redundnacy is achieved using
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that paths must be disjoint in order to be
independent.
However, under the bounded trust transitivity assumption, two non-disjoint paths
can still be independent as long as their intersection contains only trusted
nodes,
greatly increasing the level of redundancy available.
Under the bounded trust transitivity assumption, the available redundancy thus depends on
both the network structure and the level of trust.

We now quantify the {\em effective redundancy} between Alice and Bob
when trust radius $h$ is assumed.
This quantity, $\delta_{v,w,h}$ is exactly the max-flow/min-cut of
the graph after Alice's and Bob's trusted neighborhoods have been
collapsed into single source/sink vertices.
Each trust boundary forms a cut of the network and places an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(v) \mid, \mid B_h(w) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region,
an indication that the network is decentralized.
The effective redundancy of the entire graph can be characterized by the minimum over
all vertex pairs:
\beq
\delta_h(G) \equiv \min_{v,w \in V} \delta_{v,w,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be constructed between them.
$\delta_h$ is a purely structural network property,
and places an upper bound on the effectiveness of any
redundancy-based fault tolerance scheme.
The more quickly $\delta_h$ grows with $h$,
the better a network is at leveraging trust transitivity to create redundancy.
Thus, the scaling of $\delta_h$ can be used to quantify a network's ability
to withstand targeted attacks,
even when the exact trust radius $h$ is unknown.

\begin{figure}
\centerline{\includegraphics[width=3in,height=2.08in]{fig-partial-trust}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em partial trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $v$) and receiver (Bob, $w$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can be modelled as connected by a direct link with
at least $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

@@

\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {start} ( A-1.west);
\node (B1) [inner sep=1pt,above=of A-1.north,above=5ex] {\underline{A}};
\node (B2) [inner sep=1pt,above=of A-2.north,above=5ex] {\underline{B}};
\node (B3) [inner sep=1pt,above=of A-3.north,above=5ex] {\underline{C}};
\node (B4) [inner sep=1pt,above=of A-4.north,above=5ex] {\underline{D}};

@@

                outer sep=0pt, on chain, thick},

@@

\begin{theorem}
Given an $m$-bit wrap-around butterfly network ($m > 1$),
and a radius $h$ ($1 \leq h \leq \left\lfloor \frac{m}{2} \right\rfloor$),
for all node pairs $(v, w)$ such that $d(v,w) \geq 2h$,
there exist $2^h$ paths $v_s$ ($0 \le s < 2^h$) from
$v$ to $w$ such that
$s \neq s^\prime \implies v_s \cap v_{s^\prime} \subset T_h(u) \cup T_h(v)$.
\end{theorem}
\begin{proof}
Nodes from two paths can only coincide if their levels are the same.
Nodes which share a level must either be in the same stage, or 4 stages
apart.
Let ($a$,$a^\prime$) denote a pair of sub-paths corresponding to stage $a$ of
one path and stage $a^\prime$ of another.
Excluding paths that intersect in their trusted neighborhoods, (1,1) and (7,7),
we have reduced the list of possible intersections to the following cases:
(2,2), (3,3), (4,4), (5,5), (6,6), (1,5), (2,6), and (3,7).
Nodes in stages 2--4 belong to $R_s$ so cannot overlap with any stage 2--4
nodes from another path, eliminating (2,2), (3,3), and (4,4).
Similarly, nodes in stages 4--6 belong to a unique $S_s$,
eliminating (5,5) and (6,6).
Nodes in stage 1 belong to $Q_{v^{(0)}}$ while those in stage 5 belong in
its complement, eliminating (1,5).
Similarly, for all $l$ in stage 2, $z^{(l)}$ is equal to $z^{(0)}$,
while in stage 6, $z^{(l)}$ is the inverse, eliminating (2,6)
This leaves only (3,7), a collision which can occur only for only one path
(with $s$ matching the first $h$ bits of $z_w$), and which enters the trusted
neighborhood in stage 3.
For this single path, we can proceed directly from stage 2 to stage 7,
eliminating the last possible collision.
\end{proof}

@@

While decentralized protocols have received much attention for their potential
fault tolerance applications,
centralized structures are always vulnerable to exploitation by non-technical means (i.e., coercion),
and there is a need for a better understanding of the relationship between network
structure and attack-tolerance.
We have proposed a network-based scheme for {\em adversarial} fault tolerance on the
butterfly topology,
utilizing a novel concurrent multipath routing algorithm.
We have also demonstrated how {\em bounded trust transitivity},
in addition to being more realistic than infinite transitivity,
provides a theoretical foundation for
quantitative analysis of the relationship between trust,
network structure, and attack tolerance.

Such attacks include many forms of censorship and surveillance,
which have important social implications.
We have already discussed two such cases:
Pakistan's inadvertant censorship of YouTube
\cite{hunter_pakistan_2008}
and the FBI's surveillance-turned-censorship of Lavabit
\cite{poulsen_edward_2013}.
The reader may wonder how our methods could be employed in scenarios
such as large-scale state-sponsored censorship.
Censorship-resistant infrastructure often replaces central servers
(e.g., the router in the 2008 YouTube incident) with multiple servers across
the world, synchronized through consensus protocols.
The {\em directory authorities} used by the Tor project
\cite{dingledine_tor:_2004} are one example.
However, the size of such authority networks is often limited by the number of
trusted relationships (degree) each node can maintain, and the inherent insecurity of
extending transitive trust to an ever-larger network.
Our work fills a much-needed gap by quantifying the connection between network-structure,
trust transitivity,
and attack-tolerance.
We provide both a theoretical framework and specific example of how network structure
can be engineered to leverage trust for a high level of attack-tolerance,
without sacrificing scalability.

Fault-tolerant network infrastructures have many direct applications.
Areas such as cryptocurrency
\cite{mazieres_stellar_2015,nakamoto_bitcoin:_2008,king_ppcoin:_2012},
secure multiparty computation
\cite{yao_protocols_1982,chaum_multiparty_1988,goldreich_how_1987},
and wireless sensor networks
\cite{khiani_comparative_2013}
have immediate need for scalable, fault-tolerant infrastructures.
Many Internet services (e.g., email, social networks, cloud storage)
are still highly centralized and vulnerable to technical and
non-technical (i.e., coercive) attacks.
Fault tolerance using {\em both}
decentralized protocols and
decentralized network structures
is one promising approach to securing these services.

We have focused primarily on adversarial faults that block or
change messages (e.g., censorship).
Existing cryptographic techniques for circumventing surveillance
are relatively mature compared to those for tolerating censorship.
However, the techniques presented in this paper
are entirely compatible with, and in some cases could enhance, existing
anti-surveillance techniques.
For example, {\em man-in-the-middle} attacks exploit a privileged
network position to attack otherwise secure cryptography,
suggesting that structural approaches can complement cryptographic ones.

While our present proposal is specific to the butterfly topology,
the multipath fault tolerance scheme could
be applied to any network that has both sufficient redundancy and a
routing algorithm to discover independent paths.
For general networks, finding all such paths is NP-hard,
but efficient, suboptimal algorithms exist
\cite{reiter_resilient_1998}.
However, we have argued that attack-tolerance requires the ability to
influence network structure and reduce reilance on single points of failure.
Our work is most applicable to cases where the need for attack-tolerance
justifies investment in deliberate infrastructure.
For example, a coalition of groups supporting free expression could use our work
to construct a censorship-resistant communication network.
In general, such groups would need to invest resources into vetting their neighbors
to establish trust, but there are scenarios in which the attack-tolerance
requirement would justify that investment.
It is also worth noting that because faulty paths can be identified in our scheme,
it may at times be appropriate to begin by assuming mutual trust and
revoking that relationship if it is violated.
Any entities dependent on the proper functioning of the network would have an incentive
to resist attack in order to maintain their ability to participate.

Our work suggests several directions for future work towards developing
practical, attack-tolerant communication infrastructure.
The development of new multipath routing algorithms on other structured
networks could achieve higher levels of redundancy.
It is also desirable to identify dynamics that give
rise to structured networks,
and to evaluate whether our results can be generalized to unstructured or
approximately structured networks.
Finally, these results could be implemented to address specific
applications, e.g., secure messaging, domain name resolution, or
anonymous web browsing.

@@

We have presented a novel concurrent multipath routing algorithm for the butterfly
topology,
as well as a scheme for using this algorithm to construct a highly attack-tolerant
virtual channel between any two nodes, even when no fully-trusted path exists
between them.
Under this scheme, the probability of an adversary causing an undetectable error
decreases exponentially with the network's effective redundancy.
The effective redundancy, in the case of the butterfly topology,
grows exponentially with the trust radius.
Furthermore, a small increase in the number of messages sent can compensate
for a large increase in the number of messages compromised by an adversary.
We have also demonstrated how the assumption of bounded trust
transitivity can enable a quantitative analysis of the
relationships between network structure, trust, and attack-tolerance.
These results are directly applicable to systems in which the link
structure can be imposed by the designer,
and more generally, provide a theoretical foundation that can be used more to evaluate
the role of network structure, trust transitivity, and effective redundancy
on attack-tolerance.

>>>>

Our main contributions are:
\begin{itemize}
\item{
We propose a novel structured multipath fault tolerance (SMFT) scheme
for extending standard fault tolerance techniques to
{\em adversarial} faults in {\em complex networks}.
We do so by modeling redundant {\em independent paths}
with {\em bounded trust transitivity} as a single virtual channel,
and show that the probability of detecting adversarial faults
approaches 1 exponentially with the number of paths;
}
\item{We prove that the number of $h$-internally vertex disjoint
paths between two nodes in a wrap-around butterfly network
increases exponentially with $h$,
and thus that the number of independent paths in a network
increases exponentially with the level of trust transitivity;
}
\item{We present a scalable and efficient concurrent
multipath routing (CMR) algorithm on the butterfly network topology,
which can be combined with SMFT to achieve a high level of attack tolerance.}
\end{itemize}

@@

Standard fault tolerance methods use redundancy to detect and correct
statistically indpendent faults.
In complex networks however, faults can be correlated when,
for example, two messages pass through the same faulty node.
For now, let us assume our sender (Alice) and receiver (Bob) are connected
by $\delta$ direct channels, with indpendent errors.
We will return to the question of constructing these channels in subsequent
sections.
For now, we concern ourselves with the question:
given that the network provides $\delta$ redundant channels between
Alice and Bob,
what is the probability that an adversary (Mal) causes an undetectable
error after causing faults in a fixed number of channels?

@@

In a more sophisticated multipath fault tolerance scheme,
Alice randomly chooses $k \leq \delta$ channels and sends a copy of
her message on each.
We assume that Mal is capable of compromising $l \leq \delta$ channels.
Since Alice chooses channels randomly,
all channels are equally likely to contain a message,
so Mal can do no better than also choosing randomly.
If $k > l$, at least one message will get through uncompromised and all
errors are detectable.
Otherwise, the probability of Mal producing an undetectable error is
the probability that all of Alice's chosen channels are compromised:
\beq
\label{eq:pf}
p_f &=& \frac{l!(\delta-k)!}{\delta!(l-k)!}.
\eeq
Letting $k=\alpha \delta$ and $l=\beta \delta$, then applying Stirling's
approximation gives:
\begin{eqnarray}
\label{eq:pf_approx}
p_f &\approx&
\frac{\sqrt{\beta(1-\alpha)}}{\sqrt{\beta-\alpha}}
\left[
    \left( \frac{\beta-\alpha}{1-\alpha} \right)^{\alpha}
    \left( \frac{\beta}{\beta-\alpha} \right)^{\beta}
    (1-\alpha)
\right]^{\delta}.
\end{eqnarray}

Figure \ref{fig:pfail} shows the value of $p_f$
as a function of $k$ and $l$.
Equation (\ref{eq:pf_approx}) shows that while $p_f$
depends on the fractions of
channels actually utilized $\alpha$ and compromised $\beta$,
it decreases exponentially with $\delta$.
This result is significant because,
as we will soon show, $\delta$
depends only on the network structure
and the strength of trust transitivity.
{\em Thus, the scheme can be effective, even when the number of channels used
$k$ is a small fraction of the channels available}.
In other words, this scheme exhibits a {\em stabilizing asymmetry:}
senders can tolerate attacks from significantly more powerful
adversaries,
as long as the network provides large $\delta$.

\begin{figure}
\centerline{\includegraphics{fig-perror}}
\caption{
The probability of an undetectable error as a function of the number of
redundant channels and the number of adversarial faults.
}
\label{fig:pfail}
\end{figure}

@@

So far, we have assumed that Alice and Bob have access to some number
$\delta$ of channels with statistically indpendent faults.
However, in real communication architectures, direct links between all
pairs of individuals not possible and messages must be routed through
a number of intermediate nodes.
In an adversarial setting,
the existence of intermediate nodes introduces two problems:
1. intermediate nodes may be compromised by the adversary and
2. faults on paths are no longer statistically independent:
two paths may pass through the same compromised node.
We show how to how to resolve these problems using a combination of network
structure and bounded trust transitivity.

Trust-based approaches to secure communication assume that some parties
cannot be compromised.
One common approach, the web of trust
\cite{zimmermann_official_1995,ferguson_practical_2003},
extends trust infinitely transitively:
Alice trusts her friends, as well as her friends' friends, and so on.
However, the assumption of infinitely transitive trust is unrealistic
\cite{christianson_why_1997}.
Furthermore, infinite trust transitivity obscures the importance of network structure,
as it depends only on whether some path exists, not the number or quality of paths.

An alternative assumption might be that each hop away from Alice in
in the network reduces the probability that a node can resist compromise
by a multiplicatve constant.
Such a situation could occur if nodes more distant from Alice are
more favorably disposed to Alice's adversary, more likely to cooperate with that
adversary, or less likely to take proactive security measures against that
adversary.
An even simpler version assumes that nodes up to some
fixed number of hops cannot be compromised, and that those beyond can.
This simplified version is still more realistic than infinite transitivity
and will be convenient for proving our results.
We now proceed to define our model formally.

@@

Now let $s \in V$ be an arbitrary sender
and $t \in V$ be an arbitrary receiver.
We assume the presence of an adversary who knows the
full structure of the network,
and who can compromise a fixed number of nodes,
gaining complete control of their behavior.
We also assume that the adversary is specifically targeting communicaiton
between $s$ and $t$ and
can compromise any node except for those trusted by $s$ or $t$.
Under these trust assumptions, adversarial faults can only occur
outside the trusted neighborhoods of $s$ and $t$:
$V \setminus \left(T_h(v) \cup T_h(w)\right)$.
We refer to this set of nodes as the {\em untrusted region}.
We now show how it is possible to communicate reliably,
even when all available paths go through the untrusted region.

@@

Our approach is to achieve fault tolerance through redundancy.
To do so, we must use only
{\em independent paths} \cite{reiter_resilient_1998},
which have no common points of failure.
Typically, it is assumed that in order to be independent,
paths must be internally vertex disjoint, i.e.,
have no nodes in common except the endpoints.
However, under the bounded trust model,
intersecting paths can still be independent if their
intersection contains only trusted nodes.
We define two paths with common endpoints
to be {\em $h$-internally vertex disjoint}
if all common vertices are less than distance $h$ from
one of the endpoints.
This condition holds if and only if two paths are indpendent
under the bounded trust model with radius $h$.

When trust radius $h$ is assumed,
the number of $h$-internally vertex disjoint paths between
two nodes $s$ and $t$ represents the number of
channels that can be constructed between them having
statistically indpendent faults.
We thus refer to this quantity as the 
{\em effective redundancy} $\delta_{s,t,h}$.
The effective redundancy can also be interpreted as the
max-flow/min-cut of a graph after each trusted neighborhood has been
collapsed into a single vertex.
The trust boundaries form a cut of the network and place an upper bound on the
min-cut:
\beq
\delta_{v,w,h} \leq \min\left( \mid B_h(s) \mid, \mid B_h(t) \mid \right).
\eeq
Equality holds when there are no bottlenecks within the untrusted region,
an indication that the network is decentralized.
The effective redundancy of the entire graph can be characterized by the minimum
over all vertex pairs:
\beq
\delta_h(G) \equiv \min_{s,t \in V} \delta_{s,t,h}.
\eeq
Thus, for any pair of nodes in the network, at least $\delta_h$ independent,
redundant paths can be constructed between them.
The more quickly $\delta_h$ grows with $h$,
the better a network is at leveraging trust transitivity to create redundancy.
Thus, the scaling of $\delta_h$ can be used to quantify a network's ability
to withstand targeted attacks,
even when the exact trust radius $h$ is unknown.

\begin{figure}
\centerline{\includegraphics[width=3in,height=2.08in]{fig-partial-trust}}
\caption{
Illustration of a trusted communication network and the network properties
used by the {\em bounded trust model}.
Edges represent mutually trusted communication links.
The sender (Alice, $s$) and receiver (Bob, $t$) trust all nodes
less than the {\em trust radius} $h$ hops away.
These nodes form their {\em trusted neighborhoods} $T_h(v)$ and $T_h(w)$.
We assume that all faults occur in the remaining nodes: the
{\em untrusted region}.
The untrusted nodes in contact with the trusted neighborhoods for the
{\em trust boundaries} $B_h(v)$ and $B_h(w)$,
which (in the absence of central bottlenecks) determine the
{\em effective redundancy} $\delta_h$ provided by the network.
Alice and Bob can achieve the same level of attack-tolerance
as if they were directly connected by $\delta_h$ redundant channels.
}
\label{fig:trust-source}
\end{figure}

\subsection{Structured Multipath Fault Tolerance}

Finding a maximal set of independent paths for an abitrary network is NP hard
\cite{reiter_resilient_1998},
posing a challenge for multipath fault tolerance.
We propose side-stepping this problem by using structured networks,
for which independent paths can be generated efficiently.
We call this approach {\em structured multipath fault tolerance} (SMFT),
and now proceed to show how it is implemented on the butterfly
network topology.

@@

\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {\underline{Stage}} ( A-1.west);

@@

                outer sep=0pt, on chain, thick, fill=blue!20!white},

@@

\begin{theorem}
Given an $m$-bit wrap-around butterfly network ($m > 1$),
and an integer $h$ ($1 \leq h \leq \left\lfloor \frac{m}{2} \right\rfloor$),
for all node pairs $(v, w)$ such that $d(v,w) \geq 2h$,
there exist at least $2^h$ $h$-internally vertex disjoint
paths $v_s$ ($0 \le s < 2^h$) from
$v$ to $w$ such that
$s \neq s^\prime \implies v_s \cap v_{s^\prime} \subset T_h(u) \cup T_h(v)$.
\end{theorem}
\begin{proof}
Nodes from two paths can only coincide if their levels are the same.
Nodes which share a level must either be in the same stage, or 4 stages
apart.
Let ($a$,$a^\prime$) denote a pair of sub-paths corresponding to stage $a$ of
one path and stage $a^\prime$ of another.
Excluding paths that intersect in their trusted neighborhoods, (1,1) and (7,7),
we have reduced the list of possible intersections to the following cases:
(2,2), (3,3), (4,4), (5,5), (6,6), (1,5), (2,6), and (3,7).
Nodes in stages 2--4 belong to $R_s$ so cannot overlap with any stage 2--4
nodes from another path, eliminating (2,2), (3,3), and (4,4).
Similarly, nodes in stages 4--6 belong to a unique $S_s$,
eliminating (5,5) and (6,6).
Nodes in stage 1 belong to $Q_{v^{(0)}}$ while those in stage 5 belong in
its complement, eliminating (1,5).
Similarly, for all $l$ in stage 2, $z^{(l)}$ is equal to $z^{(0)}$,
while in stage 6, $z^{(l)}$ is the inverse, eliminating (2,6)
This leaves only (3,7), a collision which can occur only for only one path
(with $s$ matching the first $h$ bits of $z_w$), and which enters the trusted
neighborhood in stage 3.
For this single path, we can proceed directly from stage 2 to stage 7,
eliminating the last possible collision.
\end{proof}

@@

Our work has been motivated by the vulnerability of current communications
infrastructure to surveillance and censorship,
which are often achieved by coercive targeted attacks against central nodes.
We have already discussed two such cases:
Pakistan's inadvertant censorship of YouTube
\cite{hunter_pakistan_2008}
and the FBI's surveillance-turned-censorship of Lavabit
\cite{poulsen_edward_2013}.
The reader may wonder how our methods could be employed in scenarios
such as large-scale state-sponsored censorship
\cite{xu_internet_2011}.
Censorship-resistant infrastructure often replaces central servers
(e.g., the router in the 2008 YouTube incident) with multiple servers across
the world, synchronized through consensus protocols.
The {\em directory authorities} used by the Tor project
\cite{dingledine_tor:_2004} are one example.
However, the size of such networks is limited by the number of
trusted relationships (degree) each node can maintain, and the inherent insecurity of
extending transitive trust to an ever-larger network.
Our work provides both a theoretical framework
and a specific example of how network structure
can be engineered to leverage trust for a high level of attack-tolerance,
without sacrificing scalability.

We have focused primarily on adversarial faults that block or
change messages (censorship) but our work is also relevant to
surveillance.
While cryptographic anti-surveillance techniques exist,
they remain vulnerable to man-in-the-middle attacks,
in which an intermediate node masquerades as the destination.
Such attacks can be detected if the original message reaches the true
destination unaltered,
which SMFT can help to ensure.

In its current form, our work has several limitations.
Most obviously, it requires complete control over the network structure.
However, we have shown that even partially control over network structure can
improve attack tolerance propeties.
Still a more flexible network structure is desirable.
There is also the question of how to construct such a network without a centeral
authority.
This limitation may not be as severe as it seems,
due to the nested structure of the butterfly network.
We conjecture that smaller independently-formed networks could be
merged into a single larger network without central coordination.

In addition to addressing the above limitations,
we see several potential directions for future work.
The development of new structured networks or multipath routing algorithms
could achieve higher levels of redundancy and attack-tolerance.
It is also desirable to examine how changes to social dynamics could shift
self-organized networks towards a more decentralized structure.
Finally, our results could be implemented to address specific applications, e.g.,
secure messaging, domain name resolution, or anonymous web browsing.

@@

Coercion-resistant, topological approaches to attack tolerance are needed to
address the current vulnerability of communications infrastructure to
censorship and surveillance.
We have presented a novel concurrent multipath routing (CMR)
algorithm for the butterfly network,
as well as a structured multipath fault tolerance (SMFT) scheme,
which can be combined to create a coercion-resistant,
attack-tolerant point-to-point communication architecture.
We have also shown how assuming bounded trust
transitivity can enable a quantitative analysis of the
relationships between network structure, trust, and attack-tolerance.
In our architecture,
the probability of an adversary causing an undetectable error
decreases exponentially with the network's effective redundancy.
The effective redundancy, in the case of the butterfly topology,
grows exponentially with the radius of trust transitivity.
Furthermore, a small increase in the number of messages sent can compensate
for a large increase in the number of messages compromised by an adversary.
These results are directly applicable to systems in which the link
structure can be imposed by the designer.
Even when network structure cannot be perfectly controlled,
we have shown that partially rewiring a snapshot of the internet's router network
can greatly increase its attack-tolerance properties.
We believe that this work provides a foundation for the
development of additional topology-based communication
architectures to guard against technical and coercive adversarial attacks,
including censorship and surveillance.
